Dataflow-Guided Filtering for Efficient and Adjustable Run-Time Monitoring

### 2014-05-29 arch.tex
Reorganized paper to unify discussion of dataflow engine.

\section{Monitoring Architecture Model}
\label{sec:arch}

% Run-time monitoring overview
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/monitoring_architecture.pdf}
    \vspace{-0.2in}
    \caption{Overview of run-time monitoring architecture.}
    \label{fig:arch.overview} 
    \vspace{-0.2in}
  \end{center}
\end{figure}

Figure~\ref{fig:arch.overview} shows an overview of the run-time monitoring
model that is assumed in this paper. 
% The \emph{main task} is a computation task that performs the original function
% of the real-time system and is run on the \emph{main core}. 
The \emph{main program} is a computation task that performs the original
function of the system and is run on the \emph{main core}.
% The main task has a
% worst-case execution time (WCET) which can be upper-bounded using a variety
% of existing techniques \cite{wcetsurvey-tecs08}. This WCET is used for timing
% analysis in the design of the real-time system. As long as the execution
% time of the main task does not exceed this bound, then all timing guarantees
% from the analysis hold.
On certain events
during the main program, such as the execution of certain types of
instructions, the \emph{monitor} performs a series of \emph{monitoring
operations}. The monitor operates in parallel to the main core. These events
are referred to as
\emph{monitoring events}. Depending on the type of a monitoring event, different
monitoring operations are executed. Monitoring events are buffered
in a FIFO
structure to decouple the running of the main core and the monitor. If the FIFO
is full, then the main core is forced to stall on a monitoring event until a
FIFO entry becomes available. For programmable monitors, these stalls are a
major source of overhead because the monitor may take several cycles to process
a single event from the main core. We refer to these stalls and other
overheads,
such as contention for shared resources, as
\emph{monitoring overheads}. If the monitor detects an %inconsistent or
undesired behavior in the monitoring events, then an error is detected. 
% We do
% not focus here on the question on how to handle such an error. However, there are
% several options on how to handle an error such as raising an exception,
% notifying the user, or switching to a simpler, more trusted main task
% \cite{sha-simplex-sw01}.

There are many possible monitoring schemes that can be implemented on this
type of fine-grained parallel monitoring architecture such as
array bound checks \cite{devietti-hardbound-asplos08}, memory protection \cite{mmp02}, 
information flow tracking \cite{suh-dift-asplos04, greathouse-testudo-micro08}, 
soft error detection \cite{argus-micro07}, data-race detection \cite{cord-hpca06}, etc.
One example is an
uninitialized memory check (UMC) where 
monitoring is used to detect when software attempts to read from a memory location that
was not previously initialized. This can be done by forwarding each load and store
instruction from the main core to the monitor.
%the memory address
%of each store and load instruction on the main core to the monitor as
%well as whether the instruction was a store or load. 
For every memory location,
the monitor keeps one bit of metadata. On a store to a
memory location, the monitor marks the corresponding metadata bit to
indicate that the memory location has been initialized. On a load,
the monitor checks that the corresponding metadata bit has
been previously marked as initialized.

There are multiple options for implementing programmable parallel monitors. For example, the
Log-Based Architecture \cite{chen08-lba} uses processor cores in a multi-core
system as monitors. The FlexCore architecture \cite{deng-flexcore-micro10}
instead uses an FPGA-fabric to implement the monitor. The approach we describe
in this paper applies to any of these parallel monitors. However, for experiments,
we model an FPGA-based monitor similar to FlexCore. 
%Specifically, this
%architecture uses an on-chip FPGA fabric to
%allow high-performance and reconfigurable run-time monitoring. 
The on-chip FPGA fabric is
used to implement the ``Monitor'' block in Figure~\ref{fig:arch.overview}
while the FIFO from the main core and metadata cache are implemented as ASICs.

>>>>

\section{Dataflow Engine for Filtering and Dropping}
\label{sec:arch}

% % Overview of inserting dataflow engine between main and monitoring core
% \begin{figure}
%   \begin{center}
%     \includegraphics[width=\linewidth]{figs/dataflow_overview.pdf}
%     \vspace{-0.2in}
%     \caption{Overview of architecture for reduced and adjustable monitoring
%     overheads.}
%     \label{fig:arch.overview} 
%     \vspace{-0.1in}
%   \end{center}
% \end{figure}

% Overview of full architecture
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/architecture_overview.pdf}
    \vspace{-0.3in}
    \caption{Block diagram of architecture for monitoring with reduced and adjustable overheads.}
    \label{fig:arch.overview}
    \vspace{-0.1in}
  \end{center}
\end{figure}

In this section, we will describe our hardware architecture for reduced
overheads by filtering out null metadata and enabling partial monitoring.
Figure~\ref{fig:arch.overview} shows a high-level block diagram of the
architecture. The basic idea is to insert hardware between the main core and
the monitoring core that will reduce the number of monitoring events that reach
the monitoring core and thus reduce the overheads of monitoring.

As in the baseline architecture from Section~\ref{sec:monitoring}, events from
the main core are first buffered in a FIFO. 
Events are first filtered out based on whether they correspond to null or
invalid metadata. A hardware dataflow engine is used to track the flow of null
and invalid metadata (Section~\ref{sec:arch.dataflow}) and decide whether
specific events can be filtered out.
Next, if the event is not filtered out, then we
check whether the event should be dropped in order to stay within the specified
overhead budget. Whenever an event is dropped, its corresponding metadata is
marked and tracked as invalid by the dataflow engine. The
dropping decision hardware is described in Section~\ref{sec:arch.dropping}.
Finally, if the event is not filtered or dropped, then it is forwarded to the
monitoring core to be processed.

\subsection{Filtering Using the Dataflow Engine}
\label{sec:arch.dataflow}

% Detailed architecture of dataflow engine
\begin{figure*}
  \begin{center}
    \includegraphics[width=\linewidth]{figs/dataflow_architecture.pdf}
    \vspace{-0.2in}
    \caption{Hardware architecture of the dataflow engine.}
    \label{fig:arch.dataflow} 
    \vspace{-0.1in}
  \end{center}
\end{figure*}

% Overview
In order to perform filtering, we need to be able to identify and track flows
of null metadata. Similarly, in order to perform partial monitoring without
false positives, we need to be able to track the flow of invalid metadata. In
order to efficiently handle these operations, we use a dedicated hardware
dataflow engine. A block diagram of the dataflow engine is shown in
Figure~\ref{fig:arch.dataflow}.

% Flags and flag storage
In order track both null metadata flows and invalid metadata flows, the
dataflow engine tracks the flow of 2-bit flags. One bit represents is used to
mark metadata as null while the other bit used to mark metadata as invalid.
Monitoring schemes typically keep metadata corresponding to the main core's
register file as well as the main core's memory space. Similarly, the dataflow
engine uses an on-chip register file to store flags for register file metadata.
In addition, a set of flags are stored that correspond to memory metadata.
These memory metadata flags are accessed through a cache and backed to main
memory. All flags are initialized as null and valid when the system starts.

% Address calculation and configuration
On a monitoring event, the dataflow engine reads in up to two flags in order to
determine whether the event can be filtered.  The flags to be read in typically correspond to the source
operands of the monitored instruction. For example, on a load, the dataflow
engine will typically read in the flags corresponding the memory location
accessed.
However, the architecture is designed such that the address of flags to be read
is calculated dynamically and can be configured depending on the monitoring
scheme. Specifically, there exists a configuration table to outputs a set of
control signals depending on the instruction type of the monitoring event.
These control signals are used to control address calculation units which
contain a simple ALU. The inputs to the ALU are information from the monitored
event and a constant that is specified from the configuration table. One common
use of this address calculation is to transform addresses from byte-addressed
to word-addressed by right shifting the passed byte-address by 2 bits.

% Filtering decision
The decision of whether an event can be filtered out is determined using a
lookup table. This filter decision table is configured by the monitoring scheme
on system initialization. The lookup table determines whether an event can be
filtered out based on the pair of input flags read and the instruction type of
the monitored event.
For example, on an ALU instruction, if both of the source operand flags
indicate that the corresponding metadata is null, then the instruction can be
filtered out. Similarly, on an ALU instruction, if either of the source operand
flags indicate that their corresponding metadata is invalid, then the
instruction can also be filtered out. This filter decision is sent to the
``Filter'' block shown in Figure~\ref{fig:arch.overview} which will simply pop
filtered entries from the FIFO and not forward them. If an entry is not
filtered, then this Filter block will pop the monitoring event entry from the
FIFO and forward it along the datapath.

% Propagating flag information
Finally, when an event is filtered out, it is necessary to propagate the flag
information for the filtered event. In addition to the decision of whether to
filter an event, the filter decision table also includes information about
whether the destination flag should be written to and what value should be
written to it. A third address calculation unit generates the write address for
this destination operand flag. For example, for an ALU instruction, this will
correspond to the destination operand of the ALU instruction. If this ALU
instruction is filtered out due to having a pair of null source operands, then
the filter decision table will indicate that the destination operand's
corresponding flag should also be marked as null. In this way, the dataflow
engine propagates the flag information forward.

\subsection{Setting Dataflow Flags}
\label{sec:arch.dropping}

Although the dataflow engine automatically propagates information about
non-null and invalid metadata, it also also requires for these flows to be
initialized. Thus, it needs interfaces for setting flags to non-null and
invalid states. These interfaces are marked in Figure~\ref{fig:arch.overview}.

Metadata is marked as non-null when the monitoring core writes a valid metadata
value. When the monitoring core performs these metadata update operations, it
also writes to the corresponding dataflow flag to mark the flag as non-null.

Flags are marked as invalid when a monitoring event is dropped due to
insufficient overhead budget. Thus, whenever a monitoring event is dropped, the
dropping hardware indicates this to the dataflow engine. The dataflow engine's
configuration is already set for the write address to correspond to the
monitoring event's destination operand. Thus, on a drop signal, the dataflow
engine simply marks this destination flag as invalid.

\subsection{Example Extensions}

### 2014-05-29 introduction.tex
Reorganized paper to unify discussion of dataflow engine.

% Section summary
This paper is organized as follows. Section~\ref{sec:monitoring} presents the
parallel run-time monitoring model that this paper assumes.
Section~\ref{sec:filter} presents our architecture that uses dataflow-guided filtering
in order to reduce monitoring overheads. In Section~\ref{sec:drop} we present
how the dataflow tracking engine can be extended to enable adjustable overheads.
Section~\ref{sec:extensions} covers example implementations of three monitoring
schemes. Section~\ref{sec:evaluation} presents our evaluation methodology and
results. Finally, we discuss related work in Section~\ref{sec:related} and
conclude in Section~\ref{sec:conclusion}.

>>>>

% Section summary
This paper is organized as follows. Section~\ref{sec:monitoring} presents the
parallel run-time monitoring model that this paper assumes.
Section~\ref{sec:optimizations} presents the high-level approach of how we aim
to reduce overheads through and Section~\ref{sec:arch} describes our
hardware architecture that supports this. Section~\ref{sec:policies}
investigates the design space for dropping decisions for partial monitoring.
Section~\ref{sec:evaluation} presents our evaluation methodology and
results. Finally, we discuss related work in Section~\ref{sec:related} and
conclude in Section~\ref{sec:conclusion}.

### 2014-05-29 policies.tex
Reorganized paper to unify discussion of dataflow engine.

\section{Enabling Coverage/Overhead Trade-off}
\label{sec:drop}

Figure~\ref{dummy} shows the overheads of array bounds check with filtering
based on clean metadata (see Section~\ref{sec:evaluation} for details on
the experimental methodology). The overheads range from XX\% to XX\%. In some
contexts, this overhead may still be considered to be too high, forcing
monitoring to be disabled. Instead, it would be useful if partial monitoring
can be done in order to provide partial protection with further reduced
overheads. In this
section, we discuss how we can selectively perform monitoring in order to
further reduce overheads.

% Overview of dropping architecture
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/drop_overview.pdf}
    \vspace{-0.3in}
    \caption{Block diagram of architecture for monitoring with adjustable overheads.}
    \label{fig:drop.overview}
    \vspace{-0.1in}
  \end{center}
\end{figure}

The goal is to be able to perform as much monitoring as possible within a specified overhead budget.
The high-level approach is to keep track of monitoring overheads at run-time
and drop monitoring operations when the overhead exceed the specified budget.
A block diagram of the architecture we will present in this section is shown in
Figure~\ref{fig:drop.overview}.  In order to limit the overheads of
monitoring, we need to first be able to track the gap between the specified
overhead budget and the monitoring overhead seen at run-time. We refer to this
as slack and discuss how we measure it in Section~\ref{sec:drop.slack}. 
Dropping monitoring operations can cause false positives which we prevent by
extending the dataflow engine to track and filter out dropped monitoring flows (see
Section~\ref{sec:drop.false_positives}).
Given that we know how much slack we have for monitoring and can drop
monitoring operations without false positives, we must decide when and which
monitoring operations to drop.  There exists some interesting trade-offs in the
policy for this dropping decision which we discuss in
Section~\ref{sec:drop.policies}.

\subsection{Measuring Overheads}
\label{sec:drop.slack}

@@

% In addition to keeping track of overheads, a policy must be developed to
% determine when monitoring event should be dropped. Complex policies involving
% multiple conditions and safety factors could be used to finely tune
% the trade off between monitoring and performance overhead. Similarly, introducing
% randomness into the policy could allow for better sampling in a cooperative
% debugging application of monitoring. Here, we present one simple
% dropping policy that is based on the accumulated slack.
% When the monitor is initialized, the monitor will load
% its needed slack in order to perform a monitoring operation into a register. When
% there is a monitoring event in the FIFO to be processed, a hardware comparator
% checks whether the accumulated slack is greater than or equal to the necessary
% slack for full monitoring. If enough slack exists, the monitor is signaled to
% perform the monitoring operation. Otherwise, the monitoring event is dropped.

\subsection{Preventing False Positives}
\label{sec:drop.false_positives}

Dropping a monitoring operation implies that some functionality of the monitor
has been lost. This may cause either false negatives, where an error that
occurs in the main program's execution is not detected, or false positives,
where the monitor incorrectly believes an error has occurred. 
% For example, a
% false positive can occur for UMC if a store monitoring event is dropped. This
% causes the store memory location to not be marked as initialized. A subsequent
% load for the memory location will incorrectly cause an error to be raised.  
For example, a false positive can occur for array bounds check if an event is
dropped that handles copying a pointer. A subsequent array access using the new
pointer will incorrectly cause an error to be raised since the new pointer's
base and bounds will not be correctly set.
We
accept false negatives as the loss in coverage that we trade off in order to
limit overheads.  However, we must safely drop monitoring events in such a way
as to avoid false positives so that the system does not incorrectly raise an
error.

In analyzing various monitoring schemes, we found that monitoring operations
are primarily of two types: \emph{checks} and \emph{metadata updates}. Monitors
\emph{check} certain properties to ensure correct main program execution and
they \emph{update} metadata for bookkeeping. Skipping a check operation can
only cause false negatives and will never cause a false positive. Therefore, we
may simply skip a check operation. Skipping an update operation can cause false
negatives but may also cause false positives. Essentially, when an update
operation is skipped, we can no longer trust the corresponding metadata.  Thus,
by associating an invalid flag with each metadata we can mark metadata that is
not correctly updated and use this information to prevent false positives.

% % Flag propagation rules for BC
% \begin{table}[tb]
%   \begin{center}
%     \begin{small}
%     \input{tabs/propagation_rules}
%     \end{small}
%     \caption{Flag propagation rules for array bounds check. A dash indicates that no
%     propagation is done while a 1 indicates that the destination flag is set.}
%     \label{tab:drop.propagation_rules}
%     \vspace{-0.2in}
%   \end{center}
% \end{table}

We can track these invalid flags by extending the dataflow engine presented in
Section~\ref{sec:filter} to keep track of an additional bit for each flag. That
is, we use the dataflow engine to track 2-bit flags in order to keep track of
both clean/dirty information as well as valid/invalid information.
Similar to filtering for clean flags, we can also filter out
monitoring operations corresponding to invalid metadata which would be useless to perform.
However, it is important that we propagate the
invalidation flag in these circumstances so that the entire flow is marked as invalid. 
In the typical case, the propagation rule used is
that if any of the source operands is marked as invalid, then the destination
operand is marked as invalid. This is slightly different than the
policy for clean flags which propagates a clean flag only if both
sources are marked as clean. 
% Table~\ref{tab:drop.propagation_rules} shows the
% propagation rules that are used for array bounds check. 
We note that
the propagation rules can be customized depending on the monitor by
reconfiguring the filter decision table.

\subsection{Dropping Decision}
\label{sec:drop.policies}

@@

\begin{figure}
  \begin{center}
  \subfloat[all-event dropping]{
    \includegraphics[width=\columnwidth]{figs/all_drop.pdf}
    \label{fig:drop.all_drop}
  }
  \vspace{-0.1in}
  \\
  \subfloat[source-event dropping]{
    \includegraphics[width=\columnwidth]{figs/source_drop.pdf}
    \label{fig:drop.source_drop}
  }
  \vspace{-0.1in}
  \\
  \subfloat[min-event dropping]{
    \includegraphics[width=\columnwidth]{figs/min_drop.pdf}
    \label{fig:drop.min_drop}
  }
  \end{center}
  \vspace{-0.2in}
  \caption{Comparison of dropping policies. Blue (dark) nodes indicate where
  dropping decisions are made.}
  \label{fig:drop.policies}
\end{figure}

One method to eliminate this wasted work is to only make dropping decisions at
the root of these metadata flows. That is, we will decide to either monitor or
not monitor an entire metadata flow. We refer to this dropping decision policy
as \emph{source-event dropping} and we refer to the previous policy of 
dropping any event as \emph{all-event dropping}.
Figures~\ref{fig:drop.all_drop} and \ref{fig:drop.source_drop} shows a
comparison of where dropping decisions are made for these two policies. Source
dropping will
result in no wasted work. However, because of the coarser-grained decision, it
may be more difficult to closely match overheads. Source dropping is expected
to work well when there are a large number of independent metadata flows.

Another possible method is to make the dropping decisions somewhere in between
source-event dropping and all-event dropping. Looking at the graph from 
Figure~\ref{fig:drop.dataflow_graph}, what we would like to do is make a
decision at event {\tt C} whether to perform monitoring on that branch of the
metadata flow. If we choose to perform monitoring, then we want to perform all
monitoring on that flow. Instead, if we choose to drop event {\tt C}, then the
entire flow is dropped with no wasted work. Similarly, dropping event {\tt F}
drops the bottom flow with no wasted work and event {\tt A} can be dropped to
drop the entire shown metadata flow with no wasted work. If the program can be
analyzed or profiled to identify these instructions which, if dropped, lead to
no wasted work, then this information can be used at run-time to minimize the
amount of wasted work. We refer to this policy as \emph{min-event dropping}.
Figure~\ref{fig:drop.min_drop} shows the points were dropping decisions are
made for this policy.
Min-event dropping is a coarser-grained decision than all-event dropping, but
finer-grained that source dropping. Thus, its ability to match overheads is
expected to sit between these other two policies. Similarly, there is still a
chance of wasted work due to strange splitting and merging metadata flow graph
shapes, but typically we expect much less wasted work than all-event 
dropping. Thus, we expect the coverage achieved by min-event dropping for a
certain overhead to fall between source and all-event dropping. These three
dropping policies create a trade-off space between coverage achieved and
ability to match an overhead target which we evaluate in detail in
Section~\ref{sec:evaluation}.

% \subsection{Multiple-Run Coverage}
% Coverage can be considered for a single or average run instance. It can also be
% measured over multiple users/runs in order to capture total bug coverage of a
% program.
% 
% The system presented so far operates in a deterministic manner and so each run
% will perform the same monitoring checks. However, we can introduce randomness
% in order to achieve different dropping patterns over runs and achieve higher
% multiple-run coverage.
% 
% Due to the multiplicative effect of randomness, long dependence flows with
% multiple points where randomness is introduced leads to a small chance that the
% entire flow is monitored. This is a significant issue for last-minute dropping
% where all events could be dropped. Min-point dropping reduces this effect by
% reducing the points where dropping decisions are made while source-dropping
% eliminates this issue entirely.
% 
% \subsection{Multi-Core Implementation}
% 
% This can be extended to mulit-core by using multiple dataflow engines and a
% similar coherency protocol as that used for data caches.

>>>>

\section{Dropping Policies}
\label{sec:policies}

In order to match an overhead budget, we need to drop a portion of the
monitoring events. In this section, we discuss how this dropping decision is
made. Specifically, we first discuss how to measure the run-time monitoring
overheads and when monitoring events need to be dropped in
Section~\ref{sec:policies.slack}. Next, we investigate how the decision of
which events to drop can create a trade-off between closely matching the
overhead target and the coverage that can be achieved.

\subsection{Measuring Monitoring Overheads}
\label{sec:policies.slack}

@@

\subsection{Dropping Decision Trade-Offs}
\label{sec:policies.events}

@@

\begin{figure}
  \begin{center}
  \subfloat[unrestricted dropping]{
    \includegraphics[width=\columnwidth]{figs/all_drop.pdf}
    \label{fig:drop.all_drop}
  }
  \vspace{-0.1in}
  \\
  \subfloat[source-only dropping]{
    \includegraphics[width=\columnwidth]{figs/source_drop.pdf}
    \label{fig:drop.source_drop}
  }
  \vspace{-0.1in}
  \\
  \subfloat[split-point dropping]{
    \includegraphics[width=\columnwidth]{figs/min_drop.pdf}
    \label{fig:drop.min_drop}
  }
  \end{center}
  \vspace{-0.2in}
  \caption{Comparison of dropping policies. Blue (dark) nodes indicate where
  dropping decisions are made.}
  \label{fig:drop.policies}
\end{figure}

One method to eliminate this wasted work is to only make dropping decisions at
the root of these metadata flows. That is, we will decide to either monitor or
not monitor an entire metadata flow. We refer to this dropping decision policy
as \emph{source-only dropping} and we refer to the previous policy of 
dropping any event as \emph{unrestricted dropping}.
Figures~\ref{fig:drop.all_drop} and \ref{fig:drop.source_drop} shows a
comparison of where dropping decisions are made for these two policies. Source
dropping will
result in no wasted work. However, because of the coarser-grained decision, it
may be more difficult to closely match overheads. Source dropping is expected
to work well when there are a large number of independent metadata flows.

Another possible method is to make the dropping decisions somewhere in between
source-only dropping and unrestricted dropping. Looking at the graph from 
Figure~\ref{fig:drop.dataflow_graph}, what we would like to do is make a
decision at event {\tt C} whether to perform monitoring on that branch of the
metadata flow. If we choose to perform monitoring, then we want to perform all
monitoring on that flow. Instead, if we choose to drop event {\tt C}, then the
entire flow is dropped with no wasted work. Similarly, dropping event {\tt F}
drops the bottom flow with no wasted work and event {\tt A} can be dropped to
drop the entire shown metadata flow with no wasted work. If the program can be
analyzed or profiled to identify these instructions which, if dropped, lead to
no wasted work, then this information can be used at run-time to minimize the
amount of wasted work. We refer to this policy as \emph{split-point dropping}.
Figure~\ref{fig:drop.min_drop} shows the points were dropping decisions are
made for this policy.
Min-event dropping is a coarser-grained decision than unrestricted dropping, but
finer-grained that source dropping. Thus, its ability to match overheads is
expected to sit between these other two policies. Similarly, there is still a
chance of wasted work due to strange splitting and merging metadata flow graph
shapes, but typically we expect much less wasted work than unrestricted 
dropping. Thus, we expect the coverage achieved by split-point dropping for a
certain overhead to fall between source and unrestricted dropping. These three
dropping policies create a trade-off space between coverage achieved and
ability to match an overhead target which we evaluate in detail in
Section~\ref{sec:evaluation}.

### 2014-05-29 related.tex
Reorganized paper to unify discussion of dataflow engine.

% Monitoring
Many monitoring schemes have been developed for various security, reliability,
debugging, and other capabilities.  As we described in
Section~\ref{sec:extensions}, there exist monitoring schemes for uninitialized
memory check \cite{mondrian-asplos02}, array bounds check
\cite{hardbound-asplos08, clause-ase07}, and dynamic information flow
tracking \cite{dift-asplos04, raksha-isca07, loki-osdi08}.
Memtracker \cite{memtracker-hpca07} uses monitoring to check for various
memory-related bugs and errors.  Control flow verification techniques perform
monitoring to check that program execution follows expected control flows
\cite{schuette-comp87, impres-dac06,
kayaalp-isca12}.  Our monitoring architecture is designed to
be generally applicable to any of these instruction-grained monitoring schemes.
In particular, our proposed architecture may be especially useful for some of
these more complex schemes which also have higher overheads.  Similarly,
although many of these schemes showed low overheads in custom hardware, our
architecture can be used to reduce the overheads when applying these schemes on
a multi-core platform.

@@

% Limited Monitoring
In terms of controlling overheads, the Quality Virtual Machine (QVM) is a
modification of the Java Virtual Machine (JVM) that supports run-time
monitoring with controllable overheads \cite{qvm-oopsla08}. Similarly, Huang et
al. created a framework for controlling the overheads of software-based
monitoring \cite{huang-sttt12}. These projects are targeting a similar problem
to the one we address in this paper. However, both projects are focused on
software-based monitoring and thus their mechanisms modify the software
monitoring framework in order to enable or disable monitoring. Instead, our
architecture provides a general hardware mechanism to control overheads of
parallel monitoring architectures. In addition, these works prevented
false positives by enabling and disabling monitoring using a source-dropping
policy. Lo et al. \cite{lo-rtas14} developed a hardware architecture to limit
monitoring in hard real-time systems. Their architecture performs all-event 
dropping in order to guarantee strict deadlines. Our system allows for a
trade-off between choosing source-event dropping, all-event dropping, or min-event
dropping depending on the needs of the designer or user which has not been
explored by these previous works.

>>>>

% Monitoring
Many monitoring schemes have been developed for various security, reliability,
debugging, and other capabilities. There exist monitoring schemes for uninitialized
memory check \cite{mondrian-asplos02}, array bounds check
\cite{hardbound-asplos08, clause-ase07}, and dynamic information flow
tracking \cite{dift-asplos04, raksha-isca07, loki-osdi08}.
Memtracker \cite{memtracker-hpca07} uses monitoring to check for various
memory-related bugs and errors.  Control flow verification techniques perform
monitoring to check that program execution follows expected control flows
\cite{schuette-comp87, impres-dac06,
kayaalp-isca12}.  Our monitoring architecture is designed to
be generally applicable to any of these instruction-grained monitoring schemes.
In particular, our proposed architecture may be especially useful for some of
these more complex schemes which also have higher overheads.  Similarly,
although many of these schemes showed low overheads in custom hardware, our
architecture can be used to reduce the overheads when applying these schemes on
a multi-core platform.

@@

% Limited Monitoring
In terms of controlling overheads, the Quality Virtual Machine (QVM) is a
modification of the Java Virtual Machine (JVM) that supports run-time
monitoring with controllable overheads \cite{qvm-oopsla08}. Similarly, Huang et
al. created a framework for controlling the overheads of software-based
monitoring \cite{huang-sttt12}. These projects are targeting a similar problem
to the one we address in this paper. However, both projects are focused on
software-based monitoring and thus their mechanisms modify the software
monitoring framework in order to enable or disable monitoring. Instead, our
architecture provides a general hardware mechanism to control overheads of
parallel monitoring architectures. In addition, these works prevented
false positives by enabling and disabling monitoring using a source-dropping
policy. Lo et al. \cite{lo-rtas14} developed a hardware architecture to limit
monitoring in hard real-time systems. Their architecture performs unrestricted 
dropping in order to guarantee strict deadlines. Our system allows for a
trade-off between choosing source-only dropping, unrestricted dropping, or split-point 
dropping depending on the needs of the designer or user which has not been
explored by these previous works.
